The security of the web improved greatly throughout the last couple of years.
HTTPS is the new default, with web browsers moving from positive to
negative security indicators that instead warn the user if a connection to a
website is unencrypted.  The ecosystem around Certificate Authorities (CAs) also
improved:
	the advent of mandatory Certificate Transparency (CT) logging---as
	enforced by commonly used web browsers---make the long-known problem of
	weakest-link security in CAs more sustainable.
However, Tor and the Firefox-based Tor Browser (TB) lacks support for CT.

\hspace{12pt}
In this paper, we present privacy-preserving and incrementally-deployable
designs that add support for CT in Tor. Our designs go beyond the
support found in web browsers like Chrome and Safari:
	we aim to detect and disclose cryptographic evidence of CA and/or
	CT log misbehavior to public scrutiny when done to man-in-the-middle or
	impersonate HTTPS connections that originated from TB.
As a starting point our base design targets CA misbehavior by sharing observed
certificates in TB with the wider CT landscape.  Associated privacy
leaks, such as browsing behaviors, are minimized using distributed reporting and
caching of encountered certificates at relays in the Tor network.

%In this paper, we present designs for privacy preserving and
%incrementally-deployable support for CT in Tor. Our designs go beyond
%the support for CT found in browsers like Google Chrome or Apple's
%Safari: we aim to do more than detect CA misbehavior supporting
%man-in-the-middle or impersonated HTTPS connections from Tor Browser.
%We also create independent public evidence of CT log misbehavior in
%support of this. Our base design shares observed certificates in Tor
%Browser with other CT logs. Associated privacy leaks of browsing
%behavior of Tor users are minimized through the use of indirect
%routing and randomized delay of certificate reporting through relays
%in the Tor network.

\hspace{12pt}
We also present two possible extensions to our base design that detects CT log
misbehavior. One extension makes a slight change to the API and operation
of CT logs, whereas the other adds more complexity to Tor but in turn completely
removes all trust placed in CT log operators.  Exposing misbehaving CT logs
is important for the web in general and not just Tor, since CT as deployed today
lacks the strong mechanisms necessary to reduce trust in log operators.  We turn
Tor into a system for maintaining a probabilistically-verified view of the 
CT-landscape available from Tor’s consensus.
