\section{Related Work} \label{sec:related}
The status quo is to consider a certificate CT compliant if it is accompanied by
two independent SCTs~\cite{chrome-policy,apple-on-independence}.  Therefore we
proposed that Tor Browser should do the same, but unlike any other CT-enforcing
web browser CTor also provides concrete next steps that relax the centralized
trust which is otherwise misplaced in CT logs~\cite{%
izenpe-disqualified,%
	venafi-disqualified,%
	gdca1-omission,%
	digicert-log-compromised%
}.  Several proposals surfaced that aim to do better with regards to omissions
and split-views.

% Privacy preserving inclusion proofs
Laurie proposed that inclusion proofs could be fetched over DNS to avoid
additional privacy leaks, i.e., a user's browsing patterns are already exposed
to the DNS resolver but not the logs in the CT landscape~\cite{ct-over-dns}.
CT/bis provides the option of serving stapled inclusion proofs as part of the
TLS handshake in an extension, an OCSP response, or the certificate
itself~\cite{ct/bis}. Lueks and Goldberg proposed that a separate database of
inclusion proofs could be maintained that supports information-theoretic
PIR~\cite{lueks-and-goldberg}. Kales~\emph{et~al.} improved scalability by
reducing the size of each entry in the PIR database at the cost of transforming
logs into multi-tier Merkle trees, and additionally showed how the upper tier
could be expressed as a two-server computational PIR database to ensure that any
inclusion proof can be computed privately on-the-fly~\cite{kales}.
Nordberg~\emph{et~al.} avoid inclusion proof fetching by hanging on to presented
SFOs, handing them back to the same origin at a later time~\cite{nordberg}. In
contrast, CTor protects the user's privacy without any persistent browser state
by submitting SFOs on independent Tor circuits to CTRs, which in turn add random
noise before there is any log interaction.  The use of CTRs enable caching
similar to CT-over-DNS, but it does not put the logs in the dark like PIR could.

% The same consistent view
Inclusion proofs are only meaningful if everyone observes the same consistent
STHs. One option is to configure client software with a list of entities that
they should gossip with, e.g., CT monitors~\cite{chase}, or, browser vendors
could push a verified view~\cite{sth-push}. Such trusted auditor relationships
may work for some but not others~\cite{nordberg}. Chuat~\emph{et~al.} proposed
that HTTPS clients and HTTPS servers could pool STHs and consistency proofs,
which are gossiped on website visits~\cite{chuat}. Nordberg~\emph{et~al.}
suggested a similar variant, reducing the risk of user tracking by pooling fewer
and recent STHs~\cite{nordberg}. Dahlberg~\emph{et~al.} noted that such
privacy-insensitive STHs need not be encrypted, which could enable network
operators to use programmable data planes to provide gossip
as-a-service~\cite{dahlberg}. Syta~\emph{et~al.} proposed an alternative to
reactive gossip mechanisms by showing how an STH can be cosigned efficiently by
many independent witnesses~\cite{syta}. A smaller-scale version of witness
cosigning could be instantiated by cross-logging STHs in other CT
logs~\cite{minimal-gossip}, or in other append-only ledgers~\cite{catena}.
CTor's full design (Section~\ref{sec:base}) ensures that anyone connected to the
Tor network is on the same view by making STHs public in the Tor consensus.  In
contrast, the first incremental design (Section~\ref{sec:incremental}) is not
concerned with catching log misbehavior, while the second incremental design
(also Section~\ref{sec:incremental}) exposes misbehaving logs \emph{without}
first trying to fetch inclusion proofs.

% Other work that is closely related to our approach
Nordberg proposed that Tor clients could enforce public logging of consensus
documents and votes~\cite{consensus-transparency}.  Such an initiative is mostly
orthogonal to CTor, as it strengthens the assumption of a secure Tor consensus
by enabling detection of compromised signing keys rather than mis-issued TLS
certificates.  Winter~\emph{et~al.} proposed that Tor Browser could check
self-signed TLS certificates for exact matches on independent Tor
circuits~\cite{spoiled-onions}.  Alicherry~\emph{et~al.} proposed that any web
browser could double-check TLS certificates on first encounter using alternative
paths and Tor, again, looking for certificate mismatches and generating warnings
of possible man-in-the-middle attacks~\cite{doublecheck}.  The submission phase
in CTor is similar to double-checking, except that there are normally no TLS
handshake blocking, browser warnings, or strict assumptions regarding the
attacker's location.

% Paralell to our work
In parallel Stark and Thompson proposed that Chrome could submit a random subset
of encountered SCTs to a trusted auditor that Google runs~\cite{stark}.  CTor
also propagates a random subset of SCTs to a trusted auditor, but does so while
preserving privacy because of and how Tor is used.  Meiklejohn additionally
proposed witness cosigning on-top of consistent STHs~\cite{meiklejohn}.  CTor
adds signatures on-top of STHs too, but only as part of the Tor consensus that
directory authorities sign.
